\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-29 Proposal.tex
updating preliminaries part 1

\documentclass[twoside]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.5} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories. As such it will foster learning and could transform how we interact with course material as a whole. This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\

@@

\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution. While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

\ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting. This is the place to cite relevant literature. Where does your project extend the state of the art? what weaknesses in known approaches to you hope to overcome? If you have carried out preliminary experiments, describe them here.}

\ednote{(target size: 3-4 pages)}
\ednote {explain primitives and apply to prezi.}

\subsection{Terminology}
Information 
Knowledge
Context.

@@

In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers". The content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

@@

\subsection{Context}

Context can be easily explained with the example of Annie learning the Pythagorean theorem. The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e. calculating squares, lengths, area calculation, angles, and right angles. This is the context that the Pythagorean theorem needs.\\

Within this regard one should also consider context-sensitive and context-opaque\ednote{cite} information.

>>>>

\documentclass[twoside]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.5} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\usepackage{eurosym}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. Thus it could transform how we interact with course material and learning as a whole. This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\

@@

\newpage
\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to understand why combining spatial narrative with inherent semantic closeness might be a solution. While doing so we will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

\ednote{This part should make clear which question, exactly, you are pursuing, and why your project is relevant/interesting. Where does your project extend the state of the art? what weaknesses in known approaches to you hope to overcome?}

\subsection{Terminology}
Before we delve into the actual subject matter, we need to ensure that the terminology used is understood as intended. In the following we will use the terms information, knowledge, and context.\\

The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Looking back at the figure from section 1, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}. For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". Of special importance for us is the association. We will take this as meaning that the knowledge is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used.\\

Merriam-Webster \cite{Webster:npentrel14} defines \textbf{context} as "the parts of a discourse that surround a word or passage and can throw light on its meaning". A Context can be easily explained with the example of Annie learning the Pythagorean theorem. The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e. calculating squares, lengths, area calculation, angles, and right angles. This is the context that the Pythagorean theorem needs. We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\

@@

In \cite{LK:MathOntoAuthDoc09} it is stated that "documents consist of narrative and content layers". Here, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

@@

\ednote {explain primitives and apply to prezi.}
